% Acknowledgements

\addtocontents{toc}{} % Add a gap in the Contents, for aesthetics
\thispagestyle{empty}
\acknowledgements{

I would like to express my sincere gratitude to all those who contributed to the successful completion of this SSL Automation Tool project.

First and foremost, I extend my heartfelt thanks to \textbf{Dr. Kavari Lad}, my project guide, for his invaluable guidance, continuous support, and expert advice throughout the development of this project. His insights into modern web technologies and security practices were instrumental in shaping this work.

I am deeply grateful to \textbf{StartMySafari Innovations Private Limited (smsipl)} for providing the opportunity to work on this practical and industry-relevant project. The real-world exposure and access to modern development tools and technologies significantly enhanced my learning experience.

Special thanks to \textbf{Prof. Abhijeet Shelke}, Director, for his administrative support and for creating an environment conducive to learning and innovation.

I would like to acknowledge the faculty members of the Department of Management Science at \textbf{Dr. Babasaheb Ambedkar Marathwada University, Chhatrapati Sambhajinagar}, for their academic support and for providing the foundational knowledge that enabled me to undertake this project.

My appreciation extends to the open-source community, particularly the developers of React, Next.js, FastAPI, and Let's Encrypt, whose technologies formed the backbone of this SSL automation solution.

I am thankful to my colleagues and peers who provided feedback and suggestions during the development and testing phases of the project.

Finally, I express my gratitude to my family and friends for their constant encouragement and support throughout my academic journey.

This project has been an enriching experience that has significantly enhanced my understanding of web development, SSL certificate management, and modern software engineering practices.

\begin{flushleft}
    \textbf{\authornames}\\
    June 2025
\end{flushleft}
}
% 